Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion

### 2017-09-08 SolEnRevision_1/solar_energy_rev1.tex
Updated SolEnRevision_1 directory
Resubmitted on September 8th

\section{Introduction}
Recently, there has been strong research activity in solar thermal (ST) \cite{g1,g2}, solar thermophotovoltaic (STPV) \cite{g3,g4,g5,nnn1}, and thermophotovoltaic (TPV) \cite{g6,g7} energy conversion.  To provide a state of the art status in 
these fields, we have prepared this review article.  There is strong potential for growth in these areas, especially 
through the use of novel nanostructured surfaces to control light absorption and emission from surfaces and to 
achieve high efficiency. This spectral light control can be achieved by nanostructuring of surfaces, 
which can strongly modify their optical properties \cite{g8,g9,RF_OptExp_2009}. Recently, significant progress has been made in the modeling and fabrication of nanostructures to control optical absorption and emission properties of surfaces. 
Nanostructured surfaces, for example, can be designed to be significantly
more absorbing than their flat counterparts.
Similarly, surfaces can be designed to emit infrared radiation in a very narrow spectral range, providing spectrally selective 
surfaces~\cite{G_PS_1985, C_RPP_2014}.  Figure \ref{gfig_bbs} shows the change in 
emission spectra from a blackbody emitter to a selective emitter using optical nanostructures.
Some typical nanostructures are depicted schematically in Fig. \ref{gfig_surfs}.

STPV, ST, and TPV systems all share common surfaces but operate under different conditions.  ST and STPV systems offer an alternative to PV power generation in alternative energy systems.  Since both are heat engines, they do not adhere to the Shockley-Queisser limit and can theoretically exhibit extremely high efficiencies.  Additionally, since both ST and STPV systems rely on elements heated to high temperatures via concentrated solar energy, they are easy to modify for thermal storage of energy~\cite{SteadyStateAnalysis,Night_time_Performance}.  This would allow them to operate into the night.  An advantage of ST systems over STPV systems is that ST systems do not require the use of PV cells.  The PV cells in STPV systems are expensive and can limit overall system size.  Conversely, an advantage of STPV systems over ST systems is that STPV systems have no thermal fluid or moving parts.  This leads to them being more stable and compact solutions.  Overall, ST tends to lend itself to large, immobile power installations while STPV is better suited for small applications.  TPV systems operate on the same principle as STPV systems, but rely on an external heat source instead of solar energy~\cite{Prototype_TPV}.  This allows them to be used in energy reclamation systems.

\begin{figure}[ht!]
	\includegraphics[width=1\textwidth]{gfig_bbs}
	\caption{\label{gfig_bbs} Spectral emission of a blackbody vs. a selective emitter.  Note that the scales on each graph are in different arbitrary units; the graph is intended to show the relative narrowness of the spectrum using the selective emitter.}
\end{figure}

@@

Such control of light absorption and emission properties allows the design of high efficiency solar and thermal energy conversion devices. It also has applications in the development of 
high efficiency infrared sources, sensors, and incandescent light sources. 
Various approaches have been demonstrated for controlling light absorption and emission 
from surfaces such as the use of photonic crystals \cite{g11,NYL_SEMSC_2014,g13,g14}, 
optical metamaterials \cite{g15,g16,g17}, nanoparticles \cite{g18,g19,g20,g21}, 
multilayer thin films \cite{g22,RF_OptExp_2009} and micro/nano textured 
structures \cite{g25,g26,g27,g28}.  This review article describes various modeling methods 
available for design of optical nanostructures to control light absorption and emission properties of surfaces, the various methods available for the fabrication of large area nanostructured surfaces, and provides some examples of high-efficiency, state of the art, energy generation devices using such optical nanostructures.  A path forward to more efficient solar and thermal energy generation devices using practical design methods and fabrication techniques is examined.

@@

As the solar concentration is decreased, the ideal surface will be a blackbody absorber for wavelengths below 
some $\lambda_{cutoff}$, and an ideal reflector (generating lower emission) for wavelengths above the cutoff.  The 
location of $\lambda_{cutoff}$
depends on the temperature of the system, the power density of the emission from the emitter, and the solar concentration 
levels achieved in the system.  Typical $\lambda_{cutoff}$ values will be close to 2 $\mu m$ due to the importance of absorbing a 
large portion of the solar spectrum~\cite{RF_OptExp_2009}.

In the case of STPV systems, the emitting 
surface will also play a role in device efficiency.  The ideal
surface will be a monochromatic emitter that emits radiation with energy equal to the 
bandgap energy of the PV cell used in the system~\cite{TheoreticalEfficiency,L_AIP_2007}.  Unfortunately, monochromatic 
emitters have a power density of 0, resulting in the requirement of an infinitely large 
emitting surface for practical power generation.  Therefore, in practical STPV systems, an 
emitting surface with a small bandwidth will be desirable~\cite{RF_OptExp_2009}.  
Figure~\ref{Ideal} 
shows the evolution of maximum system efficiency vs. temperature for an ideal system.
\begin{figure}[ht!]
\begin{center}
        \includegraphics[width=0.5\textwidth]{ideal_STPV_eff}
        \caption{\label{Ideal} Maximum theoretical efficiency for various system temperatures.  Note the fast increase
around typical operation temperatures for ST and STPV systems.}
\end{center}
\end{figure}

@@

Melting point depression and thermal mismatching between layers makes temperature stability a major concern for spectrally selective surfaces.  This issue is solved primarily through material selection and the use of protective coatings on nanostructured materials \cite{paper1_ref5}.  Smaller nanostructures and thinner layers can increase this effect, resulting in a limited design space for some nanomaterials.

@@

The absorption can simply be computed as $A= 1-T-R$.  An additional requiste assumption is that the semi-infinite bounding 

@@

\subsection{Design of selective emitters for thermophotovoltaic applications using Transfer Matrix Methods}
The resonant properties of multi-layer planar structures can be exploited for designing highly-selective emitter structures for use in
thermophotovoltaic (TPV) and STPV devices.  In TPV devices, thermal energy is transferred to a 
spectrally-selective emitter
structure.  The radiation wavelength of the emitter should be well matched to a PV cell bandgap so that its thermal emission can be efficiently converted
to electrical current.  TPV systems can harvest thermal energy as waste heat from engines or other sources.  An STPV system is simply 
a TPV system that harvests thermal energy from solar radiation, and involves a good solar absorber as one of its components.
The design of both absorbers and emitter structures has been the focus of considerable theory and modeling effort.
Figure~\ref{Fan} illustrates several optimized planar emitters that were designed using Transfer Matrix Methods~\cite{BN_JApplPhys_2005, LZ_JApplPhys_2006, RF_OptExp_2009}.

@@

\section{Large area fabrication of optical nanostructures}
\subsection{Direct laser writing and laser interference lithography}
A high power laser beam focused to sub-micron dimensions allows direct 
ablation of surface material,  as shown in Figure \ref{gfig12_comb}(a), to form periodic or non-periodic structures.   Alternatively, selective exposure of a 
photoresist can create feature sizes of about 0.5 microns~\cite{g29}.

@@

\section{Solar energy conversion applications}
\subsection{Solar thermal}
Solar thermal (ST) systems are solar powered devices that generate energy via a heat engine.  Incoming solar energy is concentrated on an absorbing surface, which is heated to high temperatures.  A heat exchange fluid is then used to draw energy from the absorbing surface to the heat engine.  Since heat engines can be more efficient at higher operating temperatures, ST systems operate at high temperatures, up to 1000$^\circ$C.

@@

\subsection{Solar thermophotovoltaics}
Typical STPV systems consist of an absorbing/emitting structure that is held under vacuum to reduce convective losses and increase thermal stability~\cite{global_opt, convection}.  Then, sunlight is focused on the absorbing surface of the structure, where it is absorbed and converted into thermal energy.  This results in the absorbing/emitting structure becoming very hot, with temperatures up to 1750 K common in these systems.  As the system temperature rises, it begins to emit a large amount of thermal radiation.  The portion of thermal energy that is emitted by the emitting surface can then be collected by a PV cell and converted into electrical energy.  An additional advantage of STPV systems is their ability to store absorbed energy as heat, which is more efficient than battery storage with traditional PV cells.  STPV technology can also be easily adapted to thermophotovoltaic (TPV) systems, which operate similarly but use a burning fuel or waste heat as a thermal source instead of the sun. By transforming the incoming solar radiation from a broad-band source to a more narrow-band one, STPV systems can operate at efficiencies exceeding the Shockley-Queisser limit of 44\% for silicon PV cells operating under diffuse radiation~\cite{SQ}.  In fact, the upper {\it theoretical} limit for STPV system efficiency is 85.4\%~\cite{A2}.

\begin{table}
	\caption{Efficiency, relative solar absorption, and relative thermal emission at a temperature of 1700 K of selected absorbing surfaces.}
	\label{abs_eff_table}
	\begin{center}
		\begin{tabular}{|llll|}
			%\begin{tabular}{|p{5.3cm}|p{2.6cm}|}
			\hline
			Absorber type & Absorber efficiency & $\alpha_{sol}$ & $\epsilon_{abs}$\\
			\hline	
			Ideal solar absorber & 0.83 & 0.87 & 0.04\\
			Pseudo random nano-cones in W & 0.80 & 0.97 & 0.16~\cite{me1}\\
			W pyramidal nanostructures & 0.79 & 0.92 & 0.13~\cite{paper1_ref4}\\
			Mo-SiO$_2$ cermet & 0.77 & 0.93 & 0.16~\cite{cermet6}\\
			Carbon nanotubes & 0.74 & 0.99 & 0.95~\cite{MIT_paper,nnnNature}\\
			1-D photonic crystal on W & 0.74 & 0.80 & 0.06~\cite{SKY_JPE_2015}\\
			Blackbody absorber & 0.73 & 1.00 & 1.00\\
			Anti-reflection coating on W & 0.67 & 0.73 & 0.05~\cite{SKY_JPE_2015}\\
			W cavities & 0.59 & 0.74 & 0.15~\cite{exp_russia}\\
			Surface-relief grating on W & 0.49 & 0.53 & 0.05~\cite{paper1_ref6}\\
			Bare W & 0.41 & 0.44 & 0.04~\cite{palik}\\
			\hline
		\end{tabular}
	\end{center}
\end{table}

@@

The spectral efficiency is given by~\cite{me2}:
\begin{equation}\label{SpecEff}
SE = \frac{  \int_0^{\lambda_{bg}} \frac{ E_{bg} }{E_{\lambda}} \: B(\lambda, T) \: \epsilon_S (\lambda) \: d\lambda }
{\int_0^{\infty} B(\lambda,T) \: \epsilon_S (\lambda) \: d\lambda}
\end{equation}
where $E_{bg}$ is the bandgap energy of the PV cell, $E_{\lambda}$ is the energy of a photon with wavelength $\lambda$, and $\epsilon_S (\lambda)$ is the spectral emissivity of the emitting surface, approximated as the surface's absorptivity.  This gives the relative efficiency of the emitting surface, but does not represent an overall system efficiency.

@@

Many nanotextured emitting structures have been simulated to be extremely efficient \cite{paper2_ref13}.  These include blazed gratings on tungsten \cite{me2}, complex square gratings on tungsten \cite{paper2_ref14}, micro-cavities in tungsten \cite{paper2_ref6}, tungsten surface gratings \cite{paper1_ref6}, 3-D photonic crystals \cite{paper2_ref10}, and metamaterials \cite{meta}.  Table \ref{FOM_table} shows the spectral efficiencies of some of these surfaces.  This shows a large increase in efficiency for selective emitters over blackbody emitters.  While experimental systems using these structures have not yet been realized, they promise large efficiency gains for the future.  Table \ref{STPV_sys_table} shows the electrical efficiencies of some simulated and experimental STPV systems. 
The simulations outlined here show a large difference in predicted efficiency; however, a significant portion of this variation is caused by simulation parameters.  Since there is no standard for simulated STPV systems, some papers use an ideal model where only losses due to the surfaces are accounted for, while others use a more realistic model that encompasses many losses.  Namely, references \cite{RF_OptExp_2009} and \cite{global_opt} assume ideal PV cells, ideal solar concentrators, and assume an ideal view-factor between the emitting surface and solar cells.  References \cite{paper2_ref6}, \cite{me_thesis}, and \cite{NYL_SEMSC_2014} attempt to model PV cell losses and realistic absorbing and emitting surfaces.  Some of the remaining difference between efficiencies in the modeled systems is also due to differences in assumptions between simulations.

Despite the assumptions in these models, they clearly show that nanostructured surfaces are extremely important to ensure adequate spectral selectivity in these systems.  While reference \cite{RF_OptExp_2009} and \cite{global_opt} used many idealities, they clearly show that STPV systems are capable of having efficiencies above the Shockley-Queisser limit for single junction PV cells.  References \cite{paper2_ref6}, \cite{me_thesis}, and \cite{NYL_SEMSC_2014} predict high potential operating efficiencies using realistic operating conditions.  The primary reason that experimental systems lag behind simulations is because a lack of high quality nanostructures in these systems \cite{SKY_JPE_2015,me3}.  The YSZ and W stack used in \cite{SKY_JPE_2015} proved to be a less efficient solution for both the absorbing and emitting surfaces than other surfaces examined in this article.  In \cite{me3}, secondary, less efficient surfaces had to be used for both the absorbing and emitting structures due to fabrication problems. References \cite{SKY_JPE_2015,MIT_paper,nnnNature} uses a blackbody absorbing surface, which results in suboptimal efficiency.  Still, these devices are able to achieve very high operating efficiencies by operating at low temperatures to mitigate thermal emission from the absorber and by using nanostructured emitting surfaces.  The inclusion of an extra filter on emitted light to reduce losses in the emitting surface can also increase efficiency\cite{nnnNature}.  Still, theoretical efficiencies are much higher than experimental ones. This points to a large increase in efficiency that can be achieved by using nanostructures to close the gap between experimental and theoretical devices.  The simulation and fabrication methods outlined in this paper show that this is possible.

@@

\section{Conclusions}
We discussed a variety of modeling and fabrication techniques for controlling light 
absorption and emission by nanostructures.   Such control is important for solar and 
thermal energy conversion devices including traditional photovoltaic (PV), 
solar thermal (ST), and solar thermophotovoltaic (STPV) devices. 
The use of thermal energy conversion in particular, 
can circumvent some efficiency limitations on standard PV cells.  We 
anticipate that significant efficiency improvements can be achieved in this area 
by building on the techniques discussed here.  For example, while ST systems 
are already achieving high efficiencies in commercial use, experimental 
TPV and STPV efficiencies remain low.  The primary cause of lowered device 
efficiency is lack of control over the spectral emissivity of the 
absorbing and emitting surfaces.  The nanostructures, simulation, and 
fabrication methods highlighted here can be used to greatly increase 
efficiencies in all three of these systems.  
Indeed, simulations of nanostructured devices show that extremely high efficiencies 
exceeding the Shockley-Queisser limit are achievable in TPV/STPV systems.
For example, one of the most promising simulated devices have shown conversion efficiencies of 26.2\% at 
system temperatures of 1200$^\circ$C and a maximum conversion efficiency of 49\% was predicted for system 
temperatures of about 2130 K~\cite{RF_OptExp_2009}.  However, the highest conversion efficiency measured
for an STPV device is about 8\% for 1D photonic crystal structures of composed of tungsten and YSZ at 
device temperatures of 1640 K~\cite{SKY_JPE_2015}.  This large gap in system efficiency is due to the lack of temperature-stable 
nanostructures and high losses in experimental STPV systems.  Future theoretical design methodologies should involve
explicit considerations of aspects like thermal properties of materials and the thermal deformation of 
nanostructures to guide the fabrication of structures that are more robust to thermal degradation.    
Additionally, management strategies including the use of ST systems in tandem with STPV systems to capture waste heat from the STPV device
should be explored.

>>>>

\section{Introduction}
Recently, there has been strong research activity in solar thermal (ST) \cite{g1,g2}, solar thermophotovoltaic (STPV) \cite{g3,g4,g5,nnn1}, and thermophotovoltaic (TPV) \cite{g6,g7} \textcolor{black}{systems for converting solar and heat energy to electricity.  While hybrid PV and ST systems which convert some or all incident energy to heat for direct use (such as in a hot water heater) and in photovoltaic-thermal collectors have also seen significant advances, this review article focuses only on system which output electrical energy.  Additionally, this article focuses on high temperature STPV and ST systems due to their potentially high efficiency.}   There is strong potential for growth in these areas, especially through the use of novel nanostructured surfaces to control light absorption and emission from surfaces and to achieve high efficiency. This spectral light control can be achieved by nanostructuring of surfaces, which can strongly modify their optical properties \cite{g8,g9,RF_OptExp_2009}. Recently, significant progress has been made in the modeling and fabrication of nanostructures to control optical absorption and emission properties of surfaces. Nanostructured surfaces, for example, can be designed to be significantly more absorbing than their flat counterparts.  Similarly, surfaces can be designed to emit infrared radiation in a very narrow spectral range, providing spectrally selective surfaces~\cite{G_PS_1985, C_RPP_2014}. \textcolor{black}{ A schematic of 
an STPV device with a broad solar absorber in thermal contact with a selective emitter
is shown in Figure \ref{gfig_bbs}{\bf A}.  Figure \ref{gfig_bbs}{\bf B} and {\bf C}} show the change in emission spectra from a blackbody emitter to a selective emitter using optical nanostructures.Some typical nanostructures are depicted schematically in Fig. \ref{gfig_surfs}.

STPV, ST, and TPV systems all share common surfaces but operate under different conditions.  ST and STPV systems offer an alternative to PV power generation in alternative energy systems.  Since both are heat engines, they do not adhere to the Shockley-Queisser limit and can theoretically exhibit extremely high efficiencies.  \textcolor{black}{Additionally, since both ST and STPV systems rely on elements heated to high temperatures via concentrated solar energy, they are easy to modify for thermal storage of energy~\cite{SteadyStateAnalysis,Night_time_Performance}.  This would allow them to operate into the night.  An advantage of ST systems over STPV systems is that ST systems do not require the use of PV cells.  The PV cells in STPV systems are expensive and can limit overall system size.  Conversely, an advantage of STPV systems over ST systems is that STPV systems have no thermal fluid or moving parts.  This leads to them being more stable and compact solutions.  Overall, ST tends to lend itself to large, immobile power installations while STPV is better suited for small applications.  TPV systems operate on the same principle as STPV systems, but rely on an external heat source instead of solar energy~\cite{Prototype_TPV}.  This allows them to be used in energy reclamation systems.}

\textcolor{black}{While both ST and STPV systems are capable of exceeding the Shockley-Queisser limit in theory, only ST systems have yet been realized with high real-world efficiency~\cite{RF_OptExp_2009, RKR_RenEnRev_2013, nnnNature} .  This is due primarily to the challenges related to the extremely high temperature operation of STPV systems;
it is the view of the authors that this presents exciting opportunities for researchers in materials science, 
nanophotonics, and engineering to devise strategies for increasing the temperature stability of STPV components, 
and for increasing the performance of STPV components operating at lower temperature.  STPV systems have many advantages, such as those listed in the previous paragraph, that make them attractive for further development.}

\begin{figure}[ht!]
	\includegraphics[width=1\textwidth]{gfig_bbs_schem.png}
	\caption{\label{gfig_bbs} {\bf A} Schematic of STPV system capable of
reshaping the solar spectrum.  {\bf B} Spectral emission of a blackbody vs. {\bf C} a selective emitter.  Note that the scales on each graph are in different arbitrary units; the graph is intended to show the relative narrowness of the spectrum using the selective emitter.}
\end{figure}

@@

\textcolor{black}{Control} of light absorption and emission properties allows the design of high efficiency solar and thermal energy conversion devices. It also has applications in the development of high efficiency infrared sources, sensors, and incandescent light sources. Various approaches have been demonstrated for controlling light absorption and emission from surfaces such as the use of photonic crystals \cite{g11,NYL_SEMSC_2014,g13,g14}, optical metamaterials \cite{g15,g16,g17}, nanoparticles \cite{g18,g19,g20,g21}, multilayer thin films \cite{g22,RF_OptExp_2009} and micro/nano textured structures \cite{g25,g26,g27,g28}.  This review article describes various modeling methods available for design of optical nanostructures to control light absorption and emission properties of surfaces, the various methods available for the fabrication of large area nanostructured surfaces, and provides some examples of high-efficiency, state of the art, energy generation devices using such optical nanostructures.  A path forward to more efficient solar and thermal energy generation devices using practical design methods and fabrication techniques is examined.

@@

As the solar concentration is decreased, the ideal surface will be a blackbody absorber for wavelengths below some $\lambda_{cutoff}$, and an ideal reflector (generating lower emission) for wavelengths above the cutoff.  The location of $\lambda_{cutoff}$depends on the temperature of the system, the power density of the emission from the emitter, and the solar concentration levels achieved in the system.  Typical $\lambda_{cutoff}$ values will be close to 2 $\mu m$ due to the importance of absorbing a large portion of the solar spectrum~\cite{RF_OptExp_2009}.

In the case of STPV systems, the emitting surface will also play a role in device efficiency.  The ideal surface will be a monochromatic emitter that emits radiation with energy equal to the bandgap energy of the PV cell used in the system~\cite{TheoreticalEfficiency,L_AIP_2007}.  Unfortunately, monochromatic emitters have a power density of 0, resulting in the requirement of an infinitely large emitting surface for practical power generation.  Therefore, in practical STPV systems, an emitting surface with a small bandwidth will be desirable~\cite{RF_OptExp_2009}.  \textcolor{black}{There also will be a certain system operating temperature that will lead to maximum operating efficiency due to competing effects between Carnot efficiency and heat loss due to thermal emission from the top surface~\cite{combineLuque,concentrationGleckman}.  While it is true that the maximum thermal emission per unit area of the STPV emitter will be lower than that of the sun (because it is bounded by blackbody emission at a temperature that is lower
than the suns temperature), the area of the emitter will be much higher than the absorber in a high-efficiency STPV system.  This configuration allows STPV systems to operate with an efficiency approaching the Carnot limit in theory.  Additionally, because the output spectrum of the STPV system is well-matched to the PV cell, and thermalization losses are greatly reduced, there will be much less thermal energy absorbed by the PV cell.  This results in a lower PV cell operating temperature and a reduced requirement for cell cooling.  Figure~\ref{Ideal} shows the evolution of maximum system efficiency vs. temperature for an ideal system.  }

\begin{figure}[ht!]
\begin{center}
        \includegraphics[width=0.5\textwidth]{ideal_STPV_eff}
        \caption{\label{Ideal} Maximum theoretical efficiency for various system temperatures.  Note the fast increase
around typical operation temperatures for ST and STPV systems.}
\end{center}
\end{figure}

@@

Melting point depression and thermal mismatching between layers makes temperature stability a major concern for spectrally selective surfaces.  This issue is solved primarily through material selection and the use of protective coatings on nanostructured materials \cite{paper1_ref5}.  Smaller nanostructures and thinner layers can increase this effect, resulting in a limited design space for some nanomaterials.  \textcolor{black}{Tungsten is a commonly used material for high temperature systems due to its intrinsic thermal stability~\cite{Palik,Chaud}.  However, 
care is required when using tungsten at high temperatures as it is known to oxidize readily, and several tungsten oxides are known to melt, 
or even evaporate, at low temperatures~\cite{W_Melting}. There are several practical strategies which are effective in 
mitigating this effect.  One approach is to introduce an inert gas is done in the light bulb industry, where only a 
partial vacuum is required to eliminate oxygen and water and argon gas is used as the fill gas~\cite{Lightbulb}. 
STPV systems need to be operated in a partial vacuum to reduce convective losses regardless, so this particular strategy does not
represent an additional cost for these systems. 
Additionally, dielectric coatings on tungsten may be used to protect tungsten from oxidation~\cite{paper1_ref5}; 
in fact, the use of such coatings may be used to improves the emissive properties of tungsten as 
was the case for several high-efficiency emitter structures reported in table 2~\cite{paper1_ref5, real_efficient}.}

@@

The absorption can simply be computed as $A= 1-T-R$.  An additional requisite assumption is that the semi-infinite bounding 

@@

\subsection{Design of selective emitters for thermophotovoltaic applications using Transfer Matrix Methods}
The resonant properties of multi-layer planar structures can be exploited for designing highly-selective emitter structures for use in
thermophotovoltaic (TPV) and STPV devices.  In TPV devices, thermal energy is transferred to a 
spectrally-selective emitter
structure.  The radiation wavelength of the emitter should be well matched to a PV cell bandgap so that its thermal emission can be efficiently converted
to electrical current.  TPV systems can harvest thermal energy as waste heat from engines or other sources.  An STPV system is simply 
a TPV system that harvests thermal energy from solar radiation, and involves a good solar absorber as one of its components.
The design of both absorber and emitter structures has been the focus of considerable theory and modeling effort.
Figure~\ref{Fan} illustrates several optimized planar emitters that were designed using Transfer Matrix Methods~\cite{BN_JApplPhys_2005, LZ_JApplPhys_2006, RF_OptExp_2009}.

@@

\section{Large area fabrication of optical nanostructures}
\subsection{Direct laser writing and laser interference lithography}
A high power laser beam focused to sub-micron dimensions allows direct 
ablation of surface material,  as shown in Figure \ref{gfig12_comb}(a), to form periodic or non-periodic structures.   Alternatively, selective exposure of a 
photoresist can create feature sizes of about 0.5 microns~\cite{g29}. 
\textcolor{black}{Though these fabrication techniques are limited to structure sizes on 
the order of 1 $cm^2$, we note that in solar thermophotovoltaics
the incident sun light is highly concentrated with concentration factor of 
many 1000 times, so the focused light beam size is relatively small (less 
than an inch in diameter).  Therefore, STPV structures with relatively small
absorber and emitter components can generate reasonable power output. 
In terms of reduction of cost, one can consider utilizing an imprinting 
process using a master for low cost fabrication process.}

@@

\section{Solar energy conversion applications}
\subsection{Solar thermal}
Solar thermal (ST) systems are solar powered devices that generate energy via a heat engine.  Incoming solar energy is concentrated on an absorbing surface, which is heated to high temperatures.  A heat exchange fluid is then used to draw energy from the absorbing surface to the heat engine.  Since heat engines can be more efficient at higher operating temperatures, \textcolor{black}{it is important for ST systems to remain stable at high temperatures, up to 1000$^\circ$C.  While current TPV technology allows for high absorbance (\textgreater0.9), low thermal emission (\textless0.1), and thermal stability (in evacuated tubes) at low operating temperatures (about 400$^\circ$C), overall system efficiency can be greatly improved by increasing temperatures~\cite{ssolar,ying}.  Unfortunately, current technologies lack thermal stability and will have high thermal emission under these conditions~\cite{high_temp_review_ST}.}

@@

\subsection{Solar thermophotovoltaics}
Typical STPV systems consist of an absorbing/emitting structure that is held under vacuum to reduce convective losses and increase thermal stability~\cite{global_opt, convection}.  Then, sunlight is focused on the absorbing surface of the structure, where it is absorbed and converted into thermal energy.  This results in the absorbing/emitting structure becoming very hot, with temperatures up to 1750 K common in these systems.  As the system temperature rises, it begins to emit a large amount of thermal radiation.  The portion of thermal energy that is emitted by the emitting surface can then be collected by a PV cell and converted into electrical energy.  An additional advantage of STPV systems is their ability to store absorbed energy as heat, which is more efficient than battery storage with traditional PV cells.  STPV technology can also be easily adapted to thermophotovoltaic (TPV) systems, which operate similarly but use a burning fuel or waste heat as a thermal source instead of the sun.  \textcolor{black}{For example, there }

\textcolor{black}{By transforming the incoming solar radiation from a broad-band source to a more narrow-band one, STPV systems can operate at efficiencies exceeding the Shockley-Queisser limit of 29\% for silicon PV cells operating under diffuse radiation~\cite{scranton_from_gupta}.  This is due to the fact that the major factors that drive the Shockley-Queisser limit are losses due to below-bandgap radiation and thermalization, which are both dependent on the spectrum of light illuminating the PV cell~\cite{SQ}.  By efficiently altering the spectrum of light reaching the PV cell, the system efficiency can be increased.  In fact, the upper {\it theoretical} limit for STPV system efficiency is 85.4\%~\cite{A2}.  While reference \cite{RF_OptExp_2009} and \cite{global_opt} used many idealities, they clearly show that STPV systems are capable of having efficiencies above the Shockley-Queisser limit for single junction PV cells.  Detailed balance calculations support this conclusion as well~\cite{g5}.}

\begin{table}
	\caption{Efficiency, relative solar absorption, and relative thermal emission at a temperature of 1700 K of selected absorbing surfaces.}
	\label{abs_eff_table}
	\begin{center}
		\begin{tabular}{|llll|}
			%\begin{tabular}{|p{5.3cm}|p{2.6cm}|}
			\hline
			Absorber type & Absorber efficiency & $\alpha_{sol}$ & $\epsilon_{abs}$\\
			\hline	
			Ideal solar absorber & 0.83 & 0.87 & 0.04\\
			Pseudo random nano-cones in W & 0.80 & 0.97 & 0.16~\cite{me1}\\
			W pyramidal nanostructures & 0.79 & 0.92 & 0.13~\cite{paper1_ref4}\\
			Mo-SiO$_2$ cermet & 0.77 & 0.93 & 0.16~\cite{cermet6}\\
			Carbon nanotubes & 0.74 & 0.99 & 0.95~\cite{MIT_paper,nnnNature}\\
			1-D photonic crystal on W & 0.74 & 0.80 & 0.06~\cite{SKY_JPE_2015}\\
			Blackbody absorber & 0.73 & 1.00 & 1.00\\
			Anti-reflection coating on W & 0.67 & 0.73 & 0.05~\cite{SKY_JPE_2015}\\
			W cavities & 0.59 & 0.74 & 0.15~\cite{exp_russia}\\
			Surface-relief grating on W & 0.49 & 0.53 & 0.05~\cite{paper1_ref6}\\
			Bare W & 0.41 & 0.44 & 0.04~\cite{Palik}\\
			\hline
		\end{tabular}
	\end{center}
\end{table}

@@

The spectral efficiency is given by~\cite{me2}:
\begin{equation}\label{SpecEff}
SE = \frac{  \int_0^{\lambda_{bg}} \frac{ E_{bg} }{E_{\lambda}} \: B(\lambda, T) \: \epsilon_S (\lambda) \: d\lambda }
{\int_0^{\infty} B(\lambda,T) \: \epsilon_S (\lambda) \: d\lambda}
\end{equation}
where $E_{bg}$ is the bandgap energy of the PV cell, $E_{\lambda}$ is the energy of a photon with wavelength $\lambda$, and $\epsilon_S (\lambda)$ is the spectral emissivity of the emitting surface, approximated as the surface's absorptivity.  \textcolor{black}{This gives the relative efficiency of the emitting surface, but does not represent an overall system efficiency.  Specifically, this equation does not take into account the fill factor, open-circuit voltage, recombination losses within the PV cell, or any non-idealities in the STPV system.  The values obtained from this equation do not represent real or even potential system efficiencies, but serve as a convenient way to compare the performance of various surfaces as well as a tool for optimization.  While PV cells with external quantum efficiencies that vary by wavelength could change the optimum bandgap stated by this equation, the effect is generally small and would need to be evaluated on a case by case basis.}

@@

\textcolor{black}{Many nanotextured emitting structures have been simulated to be extremely efficient \cite{paper2_ref13}.  These include blazed gratings on tungsten \cite{me2}, complex square gratings on tungsten \cite{paper2_ref14}, micro-cavities in tungsten \cite{paper2_ref6}, tungsten surface gratings \cite{paper1_ref6}, 3-D photonic crystals \cite{paper2_ref10}, and metamaterials \cite{meta}.  Table \ref{FOM_table} shows the spectral efficiencies of some of these surfaces.  This shows a large increase in efficiency for selective emitters over blackbody emitters.  While experimental systems using these structures have not yet been realized, they promise large efficiency gains for the future.  Table \ref{STPV_sys_table} shows the electrical efficiencies of some simulated and experimental STPV systems. These efficiencies are for systems operating under AM1.5 solar simulators or real-world solar conditions.  They all are converting solar energy to usable electrical energy (work).}

The simulations outlined here show a large difference in predicted efficiency; however, a significant portion of this variation is caused by simulation parameters.  Since there is no standard for simulated STPV systems, some papers use an ideal model where only losses due to the surfaces are accounted for, while others use a more realistic model that encompasses many losses.  Namely, references \cite{RF_OptExp_2009} and \cite{global_opt} assume ideal PV cells, ideal solar concentrators, and assume an ideal view-factor between the emitting surface and solar cells.  References \cite{paper2_ref6}, \cite{me_thesis}, and \cite{NYL_SEMSC_2014} attempt to model PV cell losses and realistic absorbing and emitting surfaces.  Some of the remaining difference between efficiencies in the modeled systems is also due to differences in assumptions between simulations.

Despite the assumptions in these models, they show that nanostructured surfaces are extremely important to ensure adequate spectral selectivity in these systems.  References \cite{paper2_ref6}, \cite{me_thesis}, and \cite{NYL_SEMSC_2014} predict high potential operating efficiencies using realistic operating conditions.  The primary reason that experimental systems lag behind simulations is because a lack of high quality nanostructures in these systems \cite{SKY_JPE_2015,me3}.  The YSZ and W stack used in \cite{SKY_JPE_2015} proved to be a less efficient solution for both the absorbing and emitting surfaces than other surfaces examined in this article.  In \cite{me3}, secondary, less efficient surfaces had to be used for both the absorbing and emitting structures due to fabrication problems. References \cite{SKY_JPE_2015,MIT_paper,nnnNature} uses a blackbody absorbing surface, which results in suboptimal efficiency.  Still, these devices are able to achieve very high operating efficiencies by operating at low temperatures to mitigate thermal emission from the absorber and by using nanostructured emitting surfaces.  The inclusion of an extra filter on emitted light to reduce losses in the emitting surface can also increase efficiency\cite{nnnNature}.  Still, theoretical efficiencies are much higher than experimental ones. This points to a large increase in efficiency that can be achieved by using nanostructures to close the gap between experimental and theoretical devices.  The simulation and fabrication methods outlined in this paper show that this is possible.

@@

\section{Conclusions}
We discussed a variety of modeling and fabrication techniques for controlling light 
absorption and emission by nanostructures.   Such control is important for solar and 
thermal energy conversion devices including traditional photovoltaic (PV), 
solar thermal (ST), and solar thermophotovoltaic (STPV) devices. 
The use of thermal energy conversion in particular, 
can circumvent some efficiency limitations on standard PV cells.  \textcolor{black}{We 
anticipate that significant efficiency improvements can be achieved in this area 
by building on the techniques discussed here.  For example, while ST systems 
are already achieving high efficiencies in commercial use, experimental 
TPV and STPV efficiencies remain low.  The primary cause of lowered device 
efficiency is lack of control over the spectral emissivity of the 
absorbing and emitting surfaces.  The nanostructures, simulation, and 
fabrication methods highlighted here can be used to greatly increase 
efficiencies in all three of these systems.  
Indeed, simulations of nanostructured devices show that extremely high efficiencies 
exceeding the Shockley-Queisser limit are achievable in TPV/STPV systems.
For example, one of the most promising simulated devices have shown conversion efficiencies of 26.2\% at 
system temperatures of 1200$^\circ$C and a maximum conversion efficiency of 49\% was predicted for system 
temperatures of about 2130 K~\cite{RF_OptExp_2009}.  However, the highest conversion efficiency measured
for an STPV device is about 8\% for 1D photonic crystal structures composed of tungsten and YSZ at 
device temperatures of 1640 K~\cite{SKY_JPE_2015}.  This large gap in system efficiency is due to the lack of temperature-stable 
nanostructures and high losses in experimental STPV systems.  Future theoretical design methodologies should involve
explicit considerations of aspects like thermal properties of materials and the thermal deformation of 
nanostructures to guide the fabrication of structures that are more robust to thermal degradation.    
Additional thermal management strategies including the use of ST systems in tandem with STPV systems to capture waste heat from the STPV device
should be explored.}

\section*{Acknowledgments}
We would like to thank the NASA Langley Professor and NSF IUCRC programs for their support of this project.  Part of this work was performed at the Center for Nanoscale Materials, a U.S. Department of Energy, Office of Science, Office of Basic Energy Sciences User Facility under Contract No. DE-AC02-06CH11357.
JJF acknowledges the Center for Research at William Paterson University for financial support.
\bibliography{solar_energy_rev1}
